Software Citation Principles

### 2016-07-25 sc-principles/software-citation-principles.tex
finishing use case about generating data

\niemnote{Is this distinct from 6? Or should it be a new one?} \katznote{I think this is the same as 1, other than in 1 the research output is a paper, while here, the output is a dataset.}
This is the case where a researcher is using some software to perform an analysis, either of a physical sample or of data.
The researcher needs to know which version was used, for example in case a bug was fixed.
Note that knowing the software and its version is not sufficient to determine the ``conditions'' of the analysis, but they are essential.

@@

>>>>

This is the case where a researcher is using some software to perform an analysis, either of a physical sample or of data.
The researcher needs to know which version was used, for example in case a bug was fixed.
Note that knowing the software and its version is not sufficient to determine the ``conditions'' of the analysis, but they are essential.

@@

This is also similar to use case 1, except in that case the research output is
a paper, while here the output is a dataset.
